Fusion Moves for Correlation Clustering

### 2014-11-11 paper/egpaper_for_review.tex
shorten related work

Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
A common greedy approach is to randomly permute the nodes and than assign 
iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
Common assigning strategies are:
\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
%
The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
If the node is not assigned it construct a cluster containing the node and all its 
unassigned positively linked neighbors.  
%
Typically these algorithms started for many random permutations, 
and pick the clustering with best objective value.

>>>>

Outside computer vision greedy methods has been suggested for correlation clustering problems, see \cite{Elsner-2009} for an overview.
A common greedy approach~\cite{Soon-2001,Ng-2002,Elsner-2008} is to randomly permute the nodes and than assign 
iteratively each node to an existing cluster or create a new cluster if costs cannot be decreased by assigning to a cluster.
%Common assigning strategies are:
%\emph{BEST}; assign to cluster which is linked by the most positive edge~\cite{Ng-2002},
%\emph{FIRST}; Assign to the cluster which is first linked by a positive edge~\cite{Soon-2001}, and
%\emph{VOTE}; Assign to cluster that minimizes objective function~\cite{Elsner-2008}.
%
The PIVOT Algorithm~\cite{Ailon-2008} iterate over all nodes in random order.
If the node is not assigned it construct a cluster containing the node and all its 
unassigned positively linked neighbors.  
%
%Typically these algorithms started for many random permutations, 
%and pick the clustering with best objective value.
